Protected Areas Practical

### 2024-11-26 tutorial/MSc_PA_practical_answers.Rmd
updated rmds

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/kdh10kg/Documents/github/MSc_Protected_Areas/",
                      echo = TRUE)#
```

@@

```{r wd}
setwd("C:/Users/kdh10kg/Documents/github/MSc_Protected_Areas/")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/kdh10kg/Documents/GitHub/MSc_Protected_Areas/",
                      echo = TRUE)#
```

@@

```r
setwd("C:/Downloads/MSc_Protected_Areas-main/MSc_Protected_Areas-main/")
```
